Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-12 Arxiv/main.tex
update accuracy bound in Exponential mechanism

After post-processing, Laplace noise is discretized. Then the probability mess function for discretized Laplace mechanism is obtained by:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t-1 \leq Y < t] 
= \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

\begin{itemize}
  \item[\textbf{case 1:}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 = & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t - 1)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t)}{\Delta \bysinfer}})\\
  \end{align*}

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
We explored following accuracy bound for $\hexpmech$:
  \begin{align*}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \geq c} 
  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \geq c\}} \frac{\exp{\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)}}}{\unomalizer{\dataobs}}\\
  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
  \leq & \frac{|\candidateset| \exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|\exp{(\frac{- \epsilon}{4 S(\dataobs)})}}\\
  = & \exp{\big(\frac{ \epsilon (1 - c)}{4 S(\dataobs)}}\big)\\
  \end{align*}

@@

Unfolding the Hellinger distance in the accuracy bound, we get:

>>>>

After post-processing, Laplace noise is discretized. Then the probability mess function for discretized Laplace mechanism is obtained by:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]

Let $\betad(\alpha, \beta)$ be the true posterior distribution, i.e., $\bysinfer(\dataobs) = \betad(\alpha, \beta)$, and $r_L$ be the posterior produced by Laplace mechanism. By applying the probability mess function of discretized Laplace mechanism in our case with Hellinger distance, we get:
$$
\begin{array}{rcl}
& Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
= \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
=  \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
\end{array}
$$
where $r_L = \betad(\alpha + \lfloor Y \rfloor, \beta - \lfloor Y \rfloor)$.\\
Also, we have:
\begin{align*}
 Pr\big[\hellinger(\bysinfer(\dataobs), r_L ) 
\leq \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)\big] 
  = \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
 \end{align*}
By simplification the Hellinger distance in $\hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t)$, we get:

\begin{itemize}
  \item[\textbf{case 1:}] \textbf{t is even}\\
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  = 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}})\\
  \end{align*}

  We also have:
  \begin{align*}
  & Pr\Bigg[\hellinger(\bysinfer(\dataobs), r_L )^2 
  \leq 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}\ \Bigg] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
  \end{align*}

  \item[\textbf{case 2:}] \textbf{t is odd}\\
  let $t = 2 m + 1$
  \begin{align*}
   Pr\Bigg[ \hellinger(\bysinfer(\dataobs), r_L )^2 \leq & \\
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}\ \Bigg] \\
  \geq \quad & Pr[ - t \leq Y < t + 1] \\
  = \quad & \frac{1}{2} (1 - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}- e^{- \frac{\epsilon t}{\Delta \bysinfer}})\\
  \end{align*}

@@

\subsection{Accuracy Bound for $\hexpmech$}
\label{subsec_accuracy_smoo}
We explored following accuracy bound for $\hexpmech$:

\begin{itemize}
  \item[\textbf{lower bound}]
  \begin{align*}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) \leq c} 
  = & \sum\limits_{\{r | \hellinger(\bysinfer(\dataobs), r) \leq c\}} \frac{\exp{(\frac{- \epsilon \hellinger(\bysinfer(\dataobs), r)}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}\\
  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{\unomalizer{\dataobs}}\\
  \geq & \frac{\exp{(\frac{- \epsilon c}{4 S(\dataobs)}})}{|\candidateset|},
  \end{align*}

  Also, we have:
  \begin{align*}
  \hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c} 
  = & \frac{2 \exp{(\frac{- \epsilon c}{4 S(\dataobs)})}}{\unomalizer{\dataobs}}
  \end{align*}

  in the Bate-binomial model.\\
  Unfolding the Hellinegr distance in this accuracy bound:\\
  $c = \hellinger(\betad(\alpha, \beta), \betad(\alpha + t, \beta - t) = $
  \begin{align*}
  & 1 - \prod_{k = 0}^{\frac{t}{2} - 1}
  \sqrt{1 - \frac{\frac{t}{2}}{a + k + \frac{t}{2}}}
  \cdot
  \prod_{k = 1}^{\frac{t}{2}}
  \sqrt{1 - \frac{\frac{t}{2}}{\beta - k}}
  \end{align*}
  when t is even, and when t is odd, let $t = 2 m + 1$:
  \begin{align*}
  \qquad &
  1 - \frac{1}{\sqrt{1 + \frac{1}{2\alpha}}} \cdot 
  \sqrt{\frac{1}{\alpha + 2m} + \frac{- 2m - 1}{\beta(\alpha + 2m)}} \\
  \qquad &\cdot 
  \prod_{k = 0}^{m-1}
  \sqrt{(1 + \frac{1}{2(\alpha + k)})
  (1 + \frac{\frac{1}{2} - m}{(\alpha + m  + k)})
  } \\
  \qquad & \cdot 
  \prod_{k = 1}^{m} 
  \sqrt{(1 + \frac{1}{2(\beta - \frac{1}{2}- k)})(1 + \frac{\frac{1}{2} - m}{(\beta - \frac{1}{2}- k)})}
  \end{align*}

@@
